---
title: "p8105_hw2_hw2861"
author: "Hongmiao Wang"
date: "2022-10-02"
output: github_document
---


```{r setup,include=FALSE }
library(tidyverse)
```



##### Question1 #####

In the first step, i import and clean the NYC_Transit_data.
```{r NYC_Transit}
NYC_Transit =read_csv("./hw2_downloadfile/NYC_Transit_Subway_Entrance_And_Exit_Data.csv",col_types = cols(Route8 = "c", Route9 = "c", Route10 = "c", Route11 = "c")) %>% 
  janitor:: clean_names() %>% 
  select(line,station_name,station_latitude,station_longitude,route1:route11,entry,vending,entrance_type,ada) %>%
  mutate(entry=recode(entry, "YES"=TRUE , "NO" = FALSE))
```

The dataset contains information about each entrance and exit for each subway station in NYC.
In the original dataset, there were 32 variables on subway stations.
I cleaned the dataset by retaining my variables of interests.A part of the variable on geographical location has been removed.
In the new dataset, It contains the variables as subway lines, station name, the latitude and longitude of the station,routes served,entry, vending,entrance type, and ADA compliance. 
In the meantime, I standardised the names of the remaining 19 variables.
And the data of the entry variable has been recoded from a character(YES vs NO) to a logical variable with "TRUE" or "FALSE".
For the dimension, There are **`r nrow(NYC_Transit)` **rows × **`r ncol(NYC_Transit)` **columns in the resulting dataset. 
These data are **NOT tidy **currently. Because there are redundant columns for route numbers.And the route numbers across 11 columns can be organised into 1 columns.
