---
title: "p8105_hw2_hw2861"
author: "Hongmiao Wang"
date: "2022-10-02"
output: github_document
---


```{r setup,include=FALSE }
library(tidyverse)
library(readxl)
```

##### Question1 #####

In the first step, i import and clean the NYC_Transit_data.
```{r NYC_Transit}
NYC_Transit =read_csv("./hw2_downloaddata/NYC_Transit_Subway_Entrance_And_Exit_Data.csv",col_types = cols(Route8 = "c", Route9 = "c", Route10 = "c", Route11 = "c")) %>% 
  janitor:: clean_names() %>% 
  select(line,station_name,station_latitude,station_longitude,route1:route11,entry,vending,entrance_type,ada) %>%
  mutate(entry=recode(entry, "YES"=TRUE , "NO" = FALSE))
```

The dataset contains information about each entrance and exit for each subway station in NYC.
In the original dataset, there were 32 variables on subway stations.
I cleaned the dataset by retaining my variables of interests.A part of the variable on geographical location has been removed.
In the new dataset, It contains the variables as subway lines, station name, the latitude and longitude of the station,routes served,entry, vending,entrance type, and ADA compliance. 
In the meantime, I standardised the names of the remaining 19 variables.
And the data of the entry variable has been recoded from a character(YES vs NO) to a logical variable with "TRUE" or "FALSE".
For the dimension, There are **`r nrow(NYC_Transit)` **rows × **`r ncol(NYC_Transit)` **columns in the resulting dataset. 
These data are **NOT tidy **currently. Because there are redundant columns for route numbers.And the route numbers across 11 columns can be organised into 1 columns.

##Further 3 question in Q1
How many distinct stations are there? 

There are **`r nrow(distinct(NYC_Transit, line, station_name))`** distinct stations


How many stations are ADA compliant?
```{r NYC_Transit_ada}
NYC_Transit_AD = filter(NYC_Transit,ada==TRUE)
NYC_Transit_AD_number = nrow(distinct(NYC_Transit_AD, line, station_name))
```
**`r NYC_Transit_AD_number`** stations are ADA compliant.


What proportion of station entrances / exits without vending allow entrance?
```{r without vending allow entrance}
NYC_Transit_vending = filter(NYC_Transit,vending == "NO",entry == TRUE)
NYC_Transit_Vending2 = filter(NYC_Transit,vending == "NO")
vending = {nrow(NYC_Transit_vending)}/{nrow(NYC_Transit_Vending2)}
```
**`r vending`**  of station entrances / exits without vending allow entrance.

##Further question in Q1
As question 1 was not scored and the answer was given. 
The standard answers have been **directly pasted** here in the next chunk.
```{r}
NYC_Transit_A=
  NYC_Transit %>% 
  pivot_longer(
    route1:route11,
    names_to = "route_num",
    values_to = "route") %>% 
  filter(route == "A") %>% 
  select(station_name, line) %>% 
  distinct

NYC_Transit_A_ada=
  NYC_Transit %>% 
  pivot_longer(
    route1:route11,
    names_to = "route_num",
    values_to = "route") %>% 
  filter(route == "A", ada == TRUE) %>% 
  select(station_name, line) %>% 
  distinct
```
How many distinct stations serve the A train? 
There are **`r nrow(NYC_Transit_A)`**  serve the A train.

Of the stations that serve the A train, There are **`r nrow(NYC_Transit_A_ada)`** are ADA compliant.




##### Question2 #####
Read and clean the Mr. Trash Wheel sheet
```{r Trash_wheel}
Trash_wheel =read_excel("./hw2_downloaddata/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",sheet = "Mr. Trash Wheel", range = "A2:N535") %>% 
  janitor:: clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(sports_balls=round(sports_balls,digits=0)) %>% 
  mutate(sports_balls=as.integer(sports_balls))
```

Read and clean the Professor Trash Wheel sheet
```{r Trash_wheel}
Professor_Trash_wheel =read_excel("./hw2_downloaddata/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",sheet = "Professor Trash Wheel", range = "A2:N117") %>% 
  janitor:: clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(sports_balls=round(sports_balls,digits=0)) %>% 
  mutate(sports_balls=as.integer(sports_balls))
```

